Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-03 main.tex
reflection mapping...

        \item 
		\mwl{Continue proof reading here.}
        We introduce a bi-Lipschitz mapping 
        \begin{align*}
            \Psi : |\calR'| \rightarrow |\calK|
        \end{align*}
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,
        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
        We define 
        \begin{align*}
            \Psi(x) 
            = 
            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
            x
            .
        \end{align*}
        One easily verifies that this defines a continuous mapping $\Psi$. 
        By the same line of thought, we see that it is invertible with inverse satisfying 
        \begin{align*}
            \Psi^{-1}(z) 
            = 
            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
            z,
            \qquad 
            z = \Psi(x)
            .
        \end{align*}
        Our previous observations enable estimates for the Jacobians. 
        We have the operator norm and determinant formulas 
        \begin{gather*}
            \matnorm{ \Jacobian\Psi(x) }
            = 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
            \right)
            \\
            \matnorm{ \Jacobian\Psi(z)^{-1} }
            = 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
            \right)^{-1},
            \\
            \det\Jacobian\Psi(x)
            =
            \left( 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \right)^{n},
            \qquad
            \det\Jacobian\Psi^{-1}(x)
            =
            \left( 
            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
            \right)^{n}
        \end{gather*}
        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
        and where 
        \begin{align*}
            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
            .
        \end{align*}
        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
        By the definition of the cosine, 
        \begin{align*}
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \leq 
            \frac{ \| x_K \| }{ \| h_{{G}} \| }
            \leq 
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            ,
            \qquad 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \leq 
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \leq 
            \frac{ \diam(G) }{ \| h_{K} \| }
            .
        \end{align*}
%         \begin{align*}
%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
%             \leq 
%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
%             .
%         \end{align*}

        The diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$.
        The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of the origin in some simplex in $\calS'$
        by scaling with $(k+1)^{-1}$. Each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$. The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$. 
        In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        It follows that $\|x_{G}\| \leq \diam(T)$.

        We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
        \begin{align*}
            \frac{\diam(T)}{ \|h_{F}\|}
            \leq  
            \aspectratio(T)
            % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
            .
        \end{align*}
        We conclude that 
        \begin{gather*}
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            \leq 
            (k+1)B_{T}
            \frac{ \diam(K) }{ \| h_{T} \| }
            \leq 
            (k+1)B_{T}
            \diameterratio(\calT)
            \frac{ \diam(T) }{ \| h_{T} \| }
            \leq 
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            ,
            \\
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(T) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(K) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{gather*}
        \begin{gather*}
            \frac{ \diam(K) }{ \| h_{{K}} \| }
            \leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            ,
            \qquad 
            \frac{ \| x_{G} \| }{ \| h_{G} \| }
            \leq 
            (k+1)B_{T}
            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            .
        \end{gather*}

@@

        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$. That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
        We calculate 
        \begin{align*}
            \|a\|
            = 
            \left\|
            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
            - 
            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
            \right\|
            &
            \leq 
            \frac{\|x_{G}\|}{\|h_{G}\|} 
            + 
            \frac{\|x_{K}\|}{\|h_{K}\|} 
            \\&
            \leq 
            (k+1) 
            \left( 1 + B_{T} \right)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{align*}

@@

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
        \mwl{TODO: not enough. Make this more explicit.}

        \item 
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
        % We briefly recapitulate why it is bi-Lipschitz.
%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
%         After application of a piecewise linear Lipschitz mapping, 
%         we can assume that $|\calK|$ is convex without loss of generality. 
%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
        The combination of the previous estimates for $\Psi$ and $\Theta$,
        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
        provide 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq  
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

        \item 
        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U $ by setting 
        \begin{align*}
            \Xi_{2} := \Psi \circ \Phi.
        \end{align*}
        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
        The combination of the previous estimates for $\Psi$ and $\Phi$ now lead to 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{2} }
            &\leq 
            \Csieb{n}{k}(\calT)
            :=
            \frac 1 4
            % \left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
            \left( 4 + (k+1) \aspectratio(T) \right)
            \cdot 
            (k+1) 
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            \\
            \matnorm{ \Jacobian \Xi_{2}^{-1} }
            &\leq  
            \Cacht{n}{k}(\calT)
            :=
            \frac 1 2
            %\left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
            \left( 4 + (k+1) \aspectratio(T) \right)
            \cdot 
            (k+1) 
            \aspectratio(\calT)
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
        \end{align*}
        We get the determinant estimate 
        \begin{align*}
            |\det(\Xi_{2})|
            &\leq 
            \Cdetsieb{n}{k}(\calT)
            :=
            \frac 1 2 
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{2}^{-1})|
            &\leq 
            \Cdetacht{n}{k}(\calT)
            :=
            2
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{2}$. 
    \end{itemize}
    The proof is complete. 
\end{proof}

>>>>

        We now describe the construction of a bi-Lipschitz mapping 
            \Psi : |\calR'| \rightarrow |\calK|.
		Recall that $\calR'$ and $\calK$ are their own respective stars around the origin,
		so they must contain an open ball around the origin. 
		\mwl{Here we need a particular result. }
		Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,
        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$ for the corresponding faces. 
        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$,
        that is, the scalar product of $x$ with either height vector is positive. 
            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
        By the same line of thought, we see that it is invertible with inverse satisfying 
            \Psi^{-1}(z) 
            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
            z,
            z = \Psi(x)
        We let $\alpha_K$ and $\alpha_{{G}}$ be the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
        and let 
            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
        The preceding auxiliary results now contribute all information on the singular values of these Jacobians:
            \matnorm{ \Jacobian\Psi(x) }
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
            \matnorm{ \Jacobian\Psi(z)^{-1} }
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
            \right)^{-1},
            \det\Jacobian\Psi(x)
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \right)^{n},
            \det\Jacobian\Psi^{-1}(x)
            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
            \right)^{n}
        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
        By the definition of the cosine, 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \frac{ \| x_K \| }{ \| h_{{G}} \| }
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \frac{ \diam(G) }{ \| h_{K} \| }
%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
%             \frac{ \| x_K \| }{ \| x_{{G}} \| }

		\mwl{Continue proof reading here.}
		We need further details to complete our estimates. 
		We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$. The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
		That estimates the quotient $\| x_K \| / \| h_K \|$. 
        % 
        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        It follows again that $\|x_{G}\| \leq \diam(T)$. 
        % 
        It remains to find a lower bound for $\| h_{G} \|$.
        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$. The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$. 
        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
        %         
%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
%         \begin{align*}
%             \frac{\diam(T)}{ \|h_{F}\|}
%             \leq  
%             \aspectratio(T)
%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
%             .
%         \end{align*}
        Putting all these technical observations together, we estimate 
        \begin{align*}
            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
            &\leq 
            (k+1)B_{T}
            \frac{ \diam(K) }{ \| h_{T} \| }
            \leq 
            (k+1)B_{T}
            \diameterratio(\calT)
            \frac{ \diam(T) }{ \| h_{T} \| }
            \leq 
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            ,
            \\
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            &\leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(T) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(K) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{align*}
        \begin{gather*}
            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
            \leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            ,
            \qquad 
            \frac{ \| x_{G} \| }{ \| h_{G} \| }
            \leq 
            (k+1)B_{T}
            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            .
        \end{gather*}

@@

        The vector $a$ is the difference between $\hat h_{G}$ and $\hat h_{K}$ after both are rescaled such that they lie on the affine hyperplane with normal vector $\hat x$. That difference has length at most $\tan(\alpha_{G}) + \tan(\alpha_{K})$.
        We calculate 
        \begin{align*}
            \|a\|
            = 
            \left\|
            \frac{\|x_{G}\|}{\|h_{G}\|} \hat h_{{G}} 
            - 
            \frac{\|x_{K}\|}{\|h_{K}\|} \hat h_K
            \right\|
            &
            \leq 
            \frac{\|x_{G}\|}{\|h_{G}\|} 
            + 
            \frac{\|x_{K}\|}{\|h_{K}\|} 
            % \\&
            \leq 
            (k+1) 
            \left( 1 + B_{T} \right)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{align*}

@@

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
        \mwl{TODO: not enough. Instead, use the homeomorphism onto a ball and estimate its Lipschitz constant.}

        \item 
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        % We briefly recapitulate why it is bi-Lipschitz.
%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
%         After application of a piecewise linear Lipschitz mapping, 
%         we can assume that $|\calK|$ is convex without loss of generality. 
%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
        The combination of the previous estimates for $\Psi$ and $\Theta$,
        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
        provide 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq  
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

        \item 
        We define another mapping $ \Xi_{2} : \underlying{\patch_{\calT}(S)} \rightarrow U $ by setting 
        \begin{align*}
            \Xi_{2} := \Psi \circ \Phi.
        \end{align*}
        It is bi-Lipschitz and preserves $\partial\underlying{\patch_{\calT}(S)} \setminus \partial T$. 
		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in \underlying{\patch_{\calT}(S)}$. 
        The combination of the previous estimates for $\Psi$ and $\Phi$ now lead to 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{2} }
            &\leq 
            \Csieb{n}{k}(\calT)
            :=
            \frac 1 4
            % \left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
            \left( 4 + (k+1) \aspectratio(T) \right)
            \cdot 
            (k+1) 
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            \\
            \matnorm{ \Jacobian \Xi_{2}^{-1} }
            &\leq  
            \Cacht{n}{k}(\calT)
            :=
            \frac 1 2
            %\left( \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } \right)
            \left( 4 + (k+1) \aspectratio(T) \right)
            \cdot 
            (k+1) 
            \aspectratio(\calT)
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
        \end{align*}
        We get the determinant estimate 
        \begin{align*}
            |\det(\Xi_{2})|
            &\leq 
            \Cdetsieb{n}{k}(\calT)
            :=
            \frac 1 2 
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{2}^{-1})|
            &\leq 
            \Cdetacht{n}{k}(\calT)
            :=
            2
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{2}$. 
    \end{itemize}
    The proof is complete. 
\end{proof}
